\documentclass{article}

% ============================================================================
% F.A.B.L.E. — NeurIPS 2026 style preprint.
% Drop-in: once you add neurips_2026.sty to this folder, comment the \usepackage
% fallbacks below and uncomment the neurips line.
%   \usepackage[preprint]{neurips_2026}
% For anonymous submission:  \usepackage{neurips_2026}
% For a workshop:            \usepackage[dblblindworkshop]{neurips_2026}
%                            \workshoptitle{Workshop Name Here}
% ============================================================================

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{array}
\usepackage{hyphenat}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning, fit, backgrounds, calc}

% Lightweight margins so the article fallback resembles the NeurIPS column width.
\usepackage[margin=1in]{geometry}

% ---- TikZ node styles for the architecture diagrams ------------------------
\tikzset{
  stage/.style   = {rectangle, rounded corners=2pt, draw=black!70, fill=blue!6,
                    minimum height=8mm, minimum width=20mm, align=center, font=\small},
  agent/.style   = {rectangle, rounded corners=2pt, draw=black!70, fill=purple!8,
                    minimum height=8mm, minimum width=20mm, align=center, font=\small},
  gov/.style     = {rectangle, rounded corners=2pt, draw=black!70, fill=green!8,
                    minimum height=8mm, minimum width=20mm, align=center, font=\small},
  store/.style   = {cylinder, shape border rotate=90, aspect=0.3, draw=black!70,
                    fill=orange!10, minimum height=11mm, minimum width=16mm,
                    align=center, font=\scriptsize},
  io/.style      = {rectangle, draw=black!70, fill=black!4, minimum height=8mm,
                    align=center, font=\small},
  flow/.style    = {-{Stealth[length=2mm]}, thick},
  dflow/.style   = {-{Stealth[length=2mm]}, thick, dashed, draw=black!55},
}

\title{F.A.B.L.E.: A Framework for Adversarial Benchmarking and \\ Logic Evaluation in Privacy-Aware Multi-Agent LLM Systems}

\author{%
  Pratik Balaji \\
  Temple University \\
  Philadelphia, PA \\
  \texttt{balajipratik8@gmail.com} \\
}
\date{}

\begin{document}

\maketitle

\begin{abstract}
We present F.A.B.L.E., a privacy-aware framework for studying how multiple language-model
agents cooperate, disagree, and converge under explicit governance constraints. Rather than
treating a model's answer as a single opaque string, F.A.B.L.E. runs two contrasting
orchestration protocols over the same evaluation harness: a lightweight three-stage
\emph{standard} pipeline (Analyst $\rightarrow$ Critic $\rightarrow$ Synthesizer) and a
six-stage \emph{adversarial} pipeline (Planner $\rightarrow$ Actor $\rightarrow$ Critic
$\rightarrow$ Validator $\rightarrow$ Refiner $\rightarrow$ Judge) with bounded
refine-and-rejudge rounds. Every request passes through a fail-closed governance layer
(regex$+$LLM PII redaction with an optional Microsoft Presidio sidecar, two-layer content
guardrails, and AES-256-GCM credential encryption), is grounded by a corrective
retrieval layer (CRAG-style relevance grading over a persisted FAISS corpus and per-user
semantic memory), and is scored by a five-dimension rubric that yields an auditable verdict.
We describe the architecture and its governance and retrieval design, and report a
preliminary head-to-head evaluation of ten runs (five prompts $\times$ two modes) measuring
verdict, rubric score, and end-to-end latency. The adversarial protocol reached a 5/5 accept
rate at the cost of roughly $2.2\times$ latency over the standard protocol's 4/5 pass rate,
illustrating the accuracy--cost trade-off the framework is built to quantify. We position
the system as a reproducible platform for measuring \emph{disagreement and synthesis}, not
only final-answer accuracy, and release the orchestration code, governance layer, and
evaluation harness as an integrated artifact.
\end{abstract}

\section{Introduction}
Language models are now deployed as assistants, evaluators, and components of autonomous
workflows, yet they still produce confidently-worded answers whose intermediate reasoning is
brittle, contradictory, or unauditable. Multi-agent arrangements---debate, critique, role
specialization---can add useful diversity, but the gains are sensitive to protocol design and
notoriously hard to inspect: majority agreement is not correctness when models share
correlated errors. At the same time, any system that touches user prompts inherits privacy
and governance obligations that are usually bolted on after the fact rather than designed in.

F.A.B.L.E.\ was built to study both problems with one apparatus. The premise is that an AI
answer should be decomposed into inspectable stages that can be benchmarked individually.
A request is sanitized, screened by safety guardrails, grounded by graded retrieval, routed
through an explicit multi-stage agent pipeline, scored against a rubric, and returned with a
verdict---after the original entities masked during sanitization are reinjected so the user
still reads a natural answer. Crucially, the framework ships two pipelines that share this
spine: a fast standard committee and a slower adversarial protocol in which a Critic and
Validator actively attack the Actor's draft and a Judge arbitrates after bounded refinement
rounds. Running both over the same harness turns ``does adversarial interaction help?'' into
a measurable question rather than a rhetorical one.

This paper reflects the system as actually implemented---the governance layer, both
pipelines, the retrieval stack, and the evaluation harness are running code, not a roadmap.
We are deliberate, however, about the scope of the empirical claims: the results here are a
single preliminary batch of ten runs over five prompts per mode, intended to demonstrate the
harness and surface the trade-off, not to establish a large-scale benchmark with statistical
guarantees.

\paragraph{Contributions.}
\begin{enumerate}[leftmargin=1.6em, itemsep=2pt]
  \item A modular, privacy-aware architecture for multi-agent LLM evaluation in which
        sanitization, guardrails, retrieval, orchestration, and scoring are separable,
        inspectable stages (Section~\ref{sec:arch}).
  \item Two contrasting orchestration protocols---a three-stage standard committee and a
        six-stage adversarial pipeline with bounded refine-and-rejudge rounds---sharing one
        governance and evaluation spine (Sections~\ref{sec:standard}--\ref{sec:adversarial}).
  \item A governance layer treated as a first-class research variable: fail-closed PII
        redaction with reinjection, two-layer guardrails, and AAD-bound credential
        encryption, validated by a 40-finding internal security audit (Section~\ref{sec:gov}).
  \item A corrective-retrieval stack (CRAG-style grading over FAISS $+$ semantic memory) and
        a golden-case reasoning cache for token/latency reduction (Section~\ref{sec:retrieval}).
  \item A reproducible evaluation harness and a preliminary ten-run, two-mode comparison on
        verdict, rubric score, and latency (Section~\ref{sec:eval}).
\end{enumerate}

\section{Related Work}
\textbf{Multi-agent reasoning.} A growing line of work has language-model agents debate,
critique, or specialize to improve answer quality, often reporting gains over single-model
baselines. The recurring caveat is that improvements depend heavily on the interaction
protocol and that consensus can mask correlated error. F.A.B.L.E.\ contributes a controlled
substrate in which a critique-driven adversarial protocol and a static committee are run side
by side under identical governance and scoring, and in which disagreement is recorded rather
than averaged away.

\textbf{LLM evaluation.} Many evaluations emphasize task accuracy or pairwise preference and
underweight intermediate structure, contradiction, or deployment-realistic governance.
F.A.B.L.E.\ complements these by scoring along five rubric dimensions and emitting a verdict
with rationale, and by making the orchestration cost (latency, round count) a reported metric
rather than an implementation detail.

\textbf{Retrieval-augmented generation.} Vector retrieval improves grounding but raises
questions about evidence trust and memory retention. F.A.B.L.E.\ adopts a corrective-RAG
posture: retrieved passages are graded for relevance, the query is rewritten and re-retrieved
when results are weak, and retrieved text is explicitly framed to agents as untrusted data
rather than instructions, mitigating indirect prompt injection.

\textbf{Privacy-aware NLP.} Input sanitization and PII redaction are usually production
concerns. Here they are part of the method: redaction changes the evidence visible to later
stages, so it is modeled and reported, with a reinjection step that restores user-facing
fidelity without persisting raw identifiers.

\section{System Architecture}
\label{sec:arch}
F.A.B.L.E.\ is a five-layer system: a Next.js/React web client; a Python (FastAPI)
orchestration core; a provider-agnostic model-access layer (OpenRouter-compatible, also
usable against any OpenAI-compatible endpoint and a no-API-key local embedder); a memory and
storage layer (FAISS for the document corpus, Supabase/pgvector for per-user semantic memory,
Amazon S3 for artifacts); and an evaluation layer (rubric scoring, verdict derivation, and a
live latency harness). The orchestration core exposes both pipelines behind a shared request
path so that sanitization, guardrails, retrieval, and reinjection are identical across modes
and only the agent topology differs.

\subsection{Standard pipeline}
\label{sec:standard}
The standard pipeline (Figure~\ref{fig:standard}) is a three-stage committee. After
governance and retrieval, an \emph{Analyst} produces a structured analysis, a \emph{Critic}
identifies gaps and unsupported claims, and a \emph{Synthesizer} produces the final answer.
The run is scored by the rubric and a PASS/WARN/FAIL verdict is derived from the rubric mean.

\begin{figure}[t]
\centering
\begin{tikzpicture}[node distance=6mm and 9mm]
  \node[io]    (in)   {User\\prompt};
  \node[gov, right=of in]    (pii)  {PII\\redact};
  \node[gov, right=of pii]   (guard){Guardrail\\pre-check};
  \node[stage, right=of guard](rag) {Agentic\\RAG};
  \node[agent, below=10mm of rag] (an) {Analyst};
  \node[agent, left=of an]  (cr) {Critic};
  \node[agent, left=of cr]  (sy) {Synthesizer};
  \node[stage, left=of sy]  (rub){Rubric\\$+$ verdict};
  \node[gov, below=10mm of rub] (re){PII\\reinject};
  \node[io, right=of re] (out){Final\\answer};

  \draw[flow] (in) -- (pii);
  \draw[flow] (pii) -- (guard);
  \draw[flow] (guard) -- (rag);
  \draw[flow] (rag) -- (an);
  \draw[flow] (an) -- (cr);
  \draw[flow] (cr) -- (sy);
  \draw[flow] (sy) -- (rub);
  \draw[flow] (rub) -- (re);
  \draw[flow] (re) -- (out);

  % side stores
  \node[store, above=7mm of rag] (corpus){FAISS\\corpus};
  \node[store, left=10mm of corpus] (mem){pgvector\\memory};
  \draw[dflow] (corpus) -- (rag);
  \draw[dflow] (mem) -- (rag);
  \node[store, below=7mm of sy] (kg){Knowledge\\graph};
  \draw[dflow] (rub) |- (kg);
\end{tikzpicture}
\caption{Standard pipeline. Green = governance, blue = system stages, purple = agents,
orange = stores. Retrieval grounds the Analyst; the completed run feeds the knowledge graph.}
\label{fig:standard}
\end{figure}

\subsection{Adversarial pipeline}
\label{sec:adversarial}
The adversarial pipeline (Figure~\ref{fig:adversarial}) shares the governance and retrieval
front-end but replaces the committee with a six-role protocol. A \emph{Planner} decomposes
the task; an \emph{Actor} drafts an answer; a \emph{Critic} attacks it for flaws; a
\emph{Validator} checks factual grounding and consistency against the (untrusted) retrieved
context; a \emph{Refiner} emits a structured fix specification; and the Actor revises. This
refine loop repeats up to a hard-capped number of rounds (default two), after which a
\emph{Judge} renders an ACCEPT/REJECT verdict with score and rationale. Role-to-model
assignment is deliberately heterogeneous to avoid correlated error across the Critic and
Refiner.

\begin{figure}[t]
\centering
\begin{tikzpicture}[node distance=5mm and 7mm]
  \node[io]    (in)   {User\\prompt};
  \node[gov, right=of in]   (pii)  {PII\\redact};
  \node[gov, right=of pii]  (guard){Guardrail};
  \node[stage, right=of guard](rag){Agentic\\RAG};

  \node[agent, right=of rag] (pl){Planner};
  \node[agent, below=9mm of pl] (ac){Actor};
  \node[agent, left=of ac] (cri){Critic};
  \node[agent, left=of cri](va){Validator};
  \node[agent, left=of va] (rf){Refiner};
  \node[agent, below=9mm of rf] (ju){Judge};
  \node[gov, right=of ju] (re){PII\\reinject};
  \node[io, right=of re] (out){Final\\answer\\$+$ verdict};

  \draw[flow] (in) -- (pii);
  \draw[flow] (pii) -- (guard);
  \draw[flow] (guard) -- (rag);
  \draw[flow] (rag) -- (pl);
  \draw[flow] (pl) -- (ac);
  \draw[flow] (ac) -- (cri);
  \draw[flow] (cri) -- (va);
  \draw[flow] (va) -- (rf);
  % refine loop back to Actor
  \draw[flow, dashed, draw=red!60] (rf) to[out=70,in=110] node[above,font=\scriptsize]{refine $\leq 2$ rounds} (ac);
  \draw[flow] (rf) -- (ju);
  \draw[flow] (ju) -- (re);
  \draw[flow] (re) -- (out);

  \node[store, above=6mm of rag] (corpus){FAISS\\corpus};
  \node[store, left=8mm of corpus] (mem){pgvector\\memory};
  \draw[dflow] (corpus) -- (rag);
  \draw[dflow] (mem) -- (rag);
  \node[store, below=6mm of ju] (gc){Golden-case\\cache};
  \draw[dflow] (ju) |- (gc);
  \draw[dflow] (gc) -| (rag);
\end{tikzpicture}
\caption{Adversarial pipeline. The Critic and Validator attack the Actor's draft; the Refiner
specifies fixes and the Actor revises for up to two rounds (red loop); the Judge arbitrates.
High-quality completed runs are promoted to the golden-case cache for later reuse.}
\label{fig:adversarial}
\end{figure}

\section{Governance and Privacy}
\label{sec:gov}
Governance is part of the method because it alters the evidence later stages see.

\textbf{PII redaction with reinjection.} Each prompt is redacted before any model call: a
regex layer catches structured identifiers (email, phone, SSN, credit-card with Luhn check,
IBAN, IP, API keys) and an optional layer---either a small LLM extractor or a Microsoft
Presidio sidecar reachable over HTTP---catches names, locations, and organizations. Detected
spans are replaced by nonce-keyed placeholders; the real values are restored by a reinjection
pass on the outgoing answer so the user sees a natural response while raw identifiers never
enter logs or memory. The pipeline is \emph{fail-closed}: if redaction cannot complete,
orchestration halts.

\textbf{Two-layer content guardrails.} A microsecond rule layer (prompt-injection patterns,
credential-exfiltration patterns, a hate-speech block list, and Unicode-normalized matching
to defeat homoglyph evasion) runs before any model call; a cheap LLM classifier handles
nuanced cases and \emph{fails to ``warn,'' never to ``allow.''} Long inputs are chunked so an
injection hidden past a truncation boundary is still screened.

\textbf{Secrets.} User-supplied provider credentials are encrypted with AES-256-GCM bound to
the owning identity via additional authenticated data, so ciphertext is not portable across
users; a versioned key scheme supports rotation.

\textbf{Audit.} An internal security review enumerated 40 findings across authentication,
tenant isolation, CSRF/CORS, PII flow, secrets, guardrails, RAG/SSRF, and deployment; all
non-accepted findings were remediated and covered by regression tests. We treat this audit as
part of the artifact's reproducibility rather than as a compliance footnote.

\section{Retrieval and Memory}
\label{sec:retrieval}
\textbf{Corrective retrieval (CRAG-lite).} Retrieval pools candidates from a persisted FAISS
document corpus and, in multi-user mode, per-user pgvector memory. An LLM grades each
candidate for relevance; if too few survive, the query is rewritten and retrieval repeats up
to a bounded number of hops. The surviving passages are injected under an explicit
``untrusted data, not instructions'' framing. This makes the previously-unused document
corpus an active part of inference and reduces context pollution relative to single-shot
top-$k$.

\textbf{Golden-case reasoning cache.} A completed run that clears a quality bar (rubric mean
above threshold and a passing verdict) is promoted to a ``golden case'' stored with its
trajectory. A new prompt that is highly similar to a golden case can be answered by adapting
the stored answer (with a cheap re-check gate) or by warm-starting the pipeline with the
stored trajectory, trading a small re-check cost for a large reduction in tokens and latency.

\textbf{Adaptive routing.} A lightweight learned router (an extreme-learning-machine
meta-scorer over run embeddings) and a knowledge graph of past runs provide model-selection
hints and prior context; these are advisory and fall back to heuristics when untrained.

\section{Evaluation}
\label{sec:eval}
\textbf{Setup.} We use a live harness that issues five fixed prompts spanning code,
arithmetic reasoning, finance, factual summarization, and creative naming, each through both
the standard (\texttt{/run}) and adversarial (\texttt{/adversarial-run}) endpoints---ten runs
total. Each run records the verdict, the five-dimension rubric mean, the completed round count
(adversarial), and end-to-end latency. Quality is scored by the rubric (accuracy, depth,
clarity, actionability, coverage); the verdict is PASS/WARN/FAIL for the standard mode
(thresholded on the rubric mean) and ACCEPT/REJECT for the adversarial mode (the Judge's
decision). Configuration: run-level summaries only, Critic $=$ \texttt{claude-3.5-haiku},
Refiner $=$ \texttt{gpt-4o-mini}, \texttt{max\_rounds} $=2$, 45\,s per-call timeout. Batch run
2026-06-13.

\textbf{Standard mode.} Table~\ref{tab:standard} reports the five standard runs: mean rubric
score 82\%, mean latency 32.8\,s, pass rate 4/5. The single non-pass was the open-ended
creative prompt (WARN, 60\%), where the rubric penalized coverage and actionability.

\begin{table}[t]
\centering
\caption{Standard pipeline (Analyst $\rightarrow$ Critic $\rightarrow$ Synthesizer), 5 runs.}
\label{tab:standard}
\begin{tabular}{@{}clccr@{}}
\toprule
Run & Prompt & Verdict & Rubric score & Latency (s) \\
\midrule
S1 & code      & PASS & 87\% & 39.9 \\
S2 & reasoning & PASS & 90\% & 22.0 \\
S3 & finance   & PASS & 92\% & 45.2 \\
S4 & factual   & PASS & 82\% & 29.0 \\
S5 & creative  & WARN & 60\% & 27.7 \\
\midrule
\multicolumn{3}{r}{\textbf{Mean}} & \textbf{82\%} & \textbf{32.8} \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Adversarial mode.} Table~\ref{tab:adversarial} reports the five adversarial runs:
mean rubric score 80\%, mean latency 72.3\,s, accept rate 5/5, every run using both refine
rounds. Notably the creative prompt that only WARNed in the standard committee was driven to
an ACCEPT (82\%) by the critique-and-refine loop, and the finance run---whose Judge output was
truncated by the token budget---was correctly recovered as ACCEPT/75\% by a field-salvage
parser rather than being silently rejected (see Section~\ref{sec:findings}).

\begin{table}[t]
\centering
\caption{Adversarial pipeline (Planner $\rightarrow$ Actor $\rightarrow$ Critic $\rightarrow$
Validator $\rightarrow$ Refiner $\rightarrow$ Judge), 5 runs.}
\label{tab:adversarial}
\begin{tabular}{@{}clcccr@{}}
\toprule
Run & Prompt & Verdict & Judge score & Rounds & Latency (s) \\
\midrule
A1 & code      & ACCEPT & 85\% & 2/2 & 78.9 \\
A2 & reasoning & ACCEPT & 85\% & 2/2 & 61.6 \\
A3 & finance   & ACCEPT & 75\% & 2/2 & 90.6 \\
A4 & factual   & ACCEPT & 75\% & 2/2 & 68.1 \\
A5 & creative  & ACCEPT & 82\% & 2/2 & 62.4 \\
\midrule
\multicolumn{4}{r}{\textbf{Mean}} & & \textbf{72.3} \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Head-to-head.} Table~\ref{tab:headtohead} summarizes the trade-off. The adversarial
protocol raised the worst-case prompt from WARN to ACCEPT and reached a 5/5 accept rate, but
at $\sim$2.2$\times$ the latency of the standard committee. Mean rubric scores are close
(82\% vs.\ 80\%), which is itself informative: the adversarial protocol's value in this batch
showed up as \emph{reduced variance and eliminated failures} rather than a higher mean,
consistent with the framing that critique-driven interaction trades cost for reliability.
We stress that $n=5$ prompts per mode in a single batch is preliminary; we report it to
demonstrate the harness and the measured trade-off, not as a statistically powered result.

\begin{table}[t]
\centering
\caption{Head-to-head summary (5 prompts per mode, single batch).}
\label{tab:headtohead}
\begin{tabular}{@{}lccc@{}}
\toprule
Mode & Pass/Accept rate & Mean score & Mean latency (s) \\
\midrule
Standard    & 4/5 & 82\% & 32.8 \\
Adversarial & 5/5 & 80\% & 72.3 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Root-cause findings during evaluation}
\label{sec:findings}
The harness doubled as a debugging instrument. Two findings are worth recording because they
affect any reproduction. First, an early adversarial batch hit the client timeout: two roles
were configured with a model ID that 404s on the provider, forcing a failed call plus fallback
retry every round, compounded by inline per-agent summarization; fixing the IDs and moving to
run-level summaries cut roughly eleven calls per run and brought peak latency to 90.6\,s.
Second, two runs initially reported REJECT/0\% when the Judge had in fact returned ACCEPT---the
JSON verdict was truncated by the token budget and the parser fell through to its reject
default. Raising the Judge budget and adding a field-level salvage parser recovered the valid
acceptances and moved the adversarial accept rate from 3/5 to 5/5.

\section{Implementation Status}
The governance layer (PII redaction with reinjection, Presidio sidecar option, two-layer
guardrails, AAD-bound encryption), both orchestration pipelines, the corrective-retrieval and
golden-case layers, the rubric/verdict evaluator, the live latency harness, and the web client
are implemented and exercised by an automated test suite. Infrastructure for containerized and
Kubernetes deployment, plus an AWS (ECS/EKS) path, is defined as infrastructure-as-code.
Preliminary: the ten-run batch is a single seed; multi-user pgvector memory and the
managed-cloud deployments are validated by code review and mocked tests rather than a live
production run. We are explicit about this boundary so the empirical claims are not overread.

\section{Limitations}
\textbf{Small evaluation.} Five prompts per mode in one batch is a demonstration, not a
benchmark; there are no confidence intervals, no human evaluation, and no comparison against
external multi-agent baselines on a standard dataset.
\textbf{Rubric and judge are model-based.} Both the rubric scorer and the adversarial Judge
are themselves LLMs and inherit their biases; verdicts should be read as structured estimates,
not ground truth.
\textbf{Provider dependence.} Although provider-agnostic in principle, runs depend on external
model availability and on the chosen role-to-model mapping.
\textbf{Privacy trade-off.} Redaction reduces exposure but can remove context useful for
reasoning; quantifying that effect is future work.
\textbf{Single-process caches.} The golden-case cache and per-identity concurrency limit are
in-process and do not yet coordinate across distributed replicas.

\section{Conclusion}
F.A.B.L.E.\ is an attempt to make multi-agent LLM workflows inspectable, governable, and
comparable from the ground up. By sharing one governance, retrieval, and scoring spine across
a fast standard committee and a slower adversarial protocol, it turns ``does adversarial
interaction help?'' into a measured question; our preliminary ten-run batch shows the
expected accuracy-for-cost trade-off, with the adversarial protocol eliminating the
standard committee's lone failure at roughly twice the latency. The contribution is the
platform and its framing---disagreement and synthesis as first-class, governance as a
research variable---together with an honest account of what is built and what remains to be
validated at scale.

\bibliographystyle{plainnat}
% \bibliography{references}

\appendix

\section{Reproducibility}
\textbf{Harness.} \texttt{scripts/eval\_runs.py} issues the five fixed prompts to
\texttt{/run} and \texttt{/adversarial-run} against a running backend, records latency and
verdict per run, and appends the results table to the project research log. \textbf{Config.}
Run-level summaries only; Critic \texttt{claude-3.5-haiku}; Refiner \texttt{gpt-4o-mini};
\texttt{adversarial\_max\_rounds}=2; 45\,s per-call timeout; client timeout 180\,s.
\textbf{Embeddings.} 384-dimensional; pluggable across a no-API-key local model
(\texttt{bge-small-en-v1.5}), OpenAI, or Gemini's OpenAI-compatible endpoint, keeping the
\texttt{vector(384)} schema and FAISS index aligned. \textbf{Determinism.} Model APIs are not
deterministic; absolute numbers will vary between batches, but the harness, prompts, and
scoring are fixed so the \emph{comparison} is reproducible.

\section{Rubric and Verdict}
Quality is scored on five dimensions---accuracy, depth, clarity, actionability, coverage. The
standard verdict thresholds the rubric mean into PASS/WARN/FAIL; the adversarial verdict is
the Judge's ACCEPT/REJECT with a numeric score and a one-paragraph rationale, parsed with a
salvage path that recovers truncated-but-valid verdicts.

\section{Security Audit Summary}
The internal review recorded 40 findings (6 critical, 14 high, 14 medium, 6 low). All
non-accepted findings were remediated---centralized tenant scoping, CSRF/CORS hardening,
fail-closed guardrails with Unicode normalization, AAD-bound credential encryption with key
rotation, SSRF protection on URL ingestion, per-identity concurrency limits, identity
revocation, and notebook-export sanitization---and covered by a dedicated regression test
module. Five low-impact items are documented as accepted risks with rationale.

\end{document}
